Disease Knowledge Transfer across Neurodegenerative Diseases

### 2018-12-12 paper/paper.tex
final small edits

\begin{abstract}
We introduce Disease Knowledge Transfer (DKT), a novel technique for transferring biomarker information between related neurodegenerative diseases. DKT infers robust multimodal biomarker trajectories in rare neurodegenerative diseases even when only limited, unimodal data is available, by transferring information from larger multimodal datasets from common neurodegenerative diseases. DKT is a joint-disease generative model of biomarker progressions, which exploits biomarker relationships that are shared across diseases. As opposed to current deep learning approaches, DKT is interpretable, which allows us to understand underlying disease mechanisms, and can also predict the future evolution of subjects instead of solving simpler control vs diseased classification tasks. Here we demonstrate DKT on Alzheimer's disease (AD) variants and its ability to predict trajectories for multimodal biomarkers in Posterior Cortical Atrophy (PCA), in lack of such data from PCA subjects. For this we train DKT on a combined dataset containing subjects with two distinct diseases and sizes of data available: 1) a larger, multimodal typical AD dataset (tAD) from the TADPOLE Challenge, and 2) a smaller unimodal Posterior Cortical Atrophy (PCA) dataset from our own centre, for which only a limited number of Magnetic Resonance Imaging (MRI) scans are available. We first show that the estimated multimodal trajectories in PCA are plausible as they agree with previous literature. We further validate DKT in two situations: (1) on synthetic data, showing that it can accurately estimate the ground truth parameters and (2) on 20 DTI scans from controls and PCA patients, showing that it has favourable performance compared to standard approaches. While we demonstrated DKT on Alzheimer's variants, we note DKT is generalisable to other forms of related neurodegenerative diseases. Our code is available online: (URL not shown yet due to double-blind submission).

@@

The estimation of accurate biomarker signatures in Alzheimer's disease (AD) and related neurodegenerative diseases is crucial for understanding underlying disease mechanisms, predicting subjects' progressions, and enrichment in clinical trials. Recently, data-driven disease progression models were proposed to reconstruct long term biomarker signatures from collections of short term individual measurements \cite{lorenzi2017disease,oxtoby2018,jedynak2012computational}. When applied to large datasets of typical AD, disease progression models have shown important benefits in understanding the earliest events in the AD cascade \cite{oxtoby2018}, quantifying biomarkers' heterogeneity \cite{young2018uncovering} and they showed improved predictions over standard approaches \cite{oxtoby2018}. However, by necessity these models require large datasets -- in addition they must be both multimodal and longitudinal. Such data is not available in rare neurodegenerative diseases. In particular, most datasets for rare neurodegenerative diseases come from local clinical centres, are unimodal (e.g. MRI only) and limited both cross-sectionally and longitudinally -- this makes the application of disease progression models extremely difficult.  Moreover, such a model estimated from common diseases such as typical AD may not generalise to specific variants. For example, in Posterior Cortical Atrophy (PCA) -- a neurodegenerative syndrome causing visual disruption -- posterior regions such as the occipital lobe are affected early, instead of the hippocampus and temporal regions that are affected early in typical AD.

The problem of limited data in medical imaging has so far been addressed through transfer learning methods. These techniques successfully used transfer learning techniques to improve the accuracy of AD diagnosis \cite{hon2017towards} or prediction of MCI conversion \cite{cheng2015domain}, but have two key limitations. First, they use deep learning or other machine learning methods, which are not interpretable and don't allow us to understand underlying disease mechanisms that are either specific to rare diseases, or shared across related diseases. Secondly, these models cannot be used to forecast the future evolution of subjects at risk of disease, which is important for selecting the right subjects in clinical trials.

We propose Disease Knowledge Transfer (DKT), a generative joint model that estimates continuous multimodal biomarker progressions for multiple neurodegenerative diseases simultaneously -- including rare neurodegenerative diseases -- and which inherently performs transfer learning between the modelled phenotypes. This is achieved by exploiting biomarker relationships that are shared across diseases, whilst accounting for differences in the spatial distribution of brain pathology. DKT is interpretable, which allows us to understand underlying disease mechanisms, and can also predict the future evolution of subjects at risk of diseases. We apply DKT on Alzheimer's variants and demonstrate its ability to predict non-MRI trajectories for patients with Posterior Cortical Atrophy, in lack of such data. This is done by fitting DKT to two datasets simultaneously: (1) the TADPOLE Challenge \cite{marinescu2018tadpole} dataset containing subjects from the Alzheimer's Disease Neuroimaging Initiative (ADNI) with MRI, FDG-PET, DTI, AV45 and AV1451 scans and (2) MRI scans from patients with Posterior Cortical Atrophy from our own centre. We first show that the estimated trajectories for PCA and tAD subjects are plausible as they agree with previous literature findings. We further validate DKT on simulated data from two synthetic diseases with known ground truth, and a set of 20 DTI scans from controls and PCA patients, showing it yields favourable performance compared to standard approaches. Code for DKT is available online: (URL not shown yet).

\begin{figure}[h]
 \centering
 \includegraphics[width=0.9\textwidth,trim=0 0 0 0,clip]{figures/disease_knowledge_transfer_symbols.pdf}
 \caption{Diagram of the proposed DKT framework. We assume that each disease can be modelled as the evolution of abstract dysfunction scores (Y-axis, top row), each one related to different brain regions. Each region-specific dysfunction score then further models (X-axis, bottom row) the progression of several modality-specific biomarkers within that same region. For instance, the temporal dysfunction, modelled as a biomarker in the disease specific model (top row), is the X-axis in the disease agnostic model (temporal unit, bottom row), which aggregates together abnormality from amyloid, tau and MR imaging within the temporal lobe. The biomarker correlations within the bottom units are assumed to be disease agnostic and shared across all diseases modelled. Disease knowledge transfer can then be achieved via the disease-agnostic units. Mathematical notation from section \ref{sec:method} is shown in red to ease understanding.}
 \label{fig:diagram}
\end{figure}

@@

The assumption that the dynamics of some biomarkers are disease-agnostic (i.e. shared across diseases), is key to DKT. There are several reasons why we can make this assumption. First of all, pathology in many related neurodegenerative diseases ( e.g. Alzheimer's variants) are hypothesized to share the same underlying mechanisms (e.g. amyloid and tau accumulation), and within one region, such accumulation leads to the same pathology dynamics across all the related disease variants: hypometabolism (FDG PET), neuronal damage (T1/DTI MRI) and region-specific cognitive decline \cite{jack2010hypothetical} -- the difference between these variants is that distinct brain regions are affected at different times and with different pathology rates and extent, likely caused by selective vulnerability of networks within these regions \cite{seeley2009neurodegenerative}. Secondly, even if the diseases share different upstream mechanisms (e.g. amyloid vs tau accumulation), downstream biomarkers measuring hypometabolism, white matter degradation and structural markers follow the same pathological cascade and will have similar dynamics across diseases.

@@

\begin{equation}
\label{eqDysfunctionScoreDef}
 \gamma_i^l = f(\beta_i + m_{ij}; \lambda_{d_i}^l)
\end{equation}
where $f$ is a smooth monotonic function mapping each disease stage to a dysfunction score, having parameters $\lambda_{d_i}^l$ corresponding to agnostic unit $l \in \Lambda$ in the disease space $d_i$ of subject $i$. We implement $f$ as a parametric sigmoidal curve similar to \cite{jedynak2012computational}, to enable a robust optimisation and because this accounts for floor and ceiling effects present in AD biomarkers. Moreover, $d_i \in \mathbb{D}$ represents the index of the disease space where subject $i$ belongs, where $\mathbb{D}$ is the set of all diseases modelled. For example, MCI and tAD subjects from ADNI as well as tAD subjects from our own cohort can all be assigned $d_i=1$, while PCA subjects from our own centre can be assigned $d_i=2$. Variable $\epsilon_k$ denotes the variance of measurements for biomarker $k$.

@@

We model the biomarker dynamics that are disease-agnostic, by constructing the mapping from the dysfunction scores $\gamma_i^l$ to the biomarker measurements. We assume a set of given biomarkers measurements $Y = [y_{ijk} | (i,j,k) \in \Omega]$ for subject $i$ at visit $j$ in biomarker $k$, where $\Omega$ is defined as the set of available biomarker measurements, since subjects can have missing biomarkers at various visits. We further denote by $\theta_k$ the trajectory parameters for biomarker $k \in K$ within its agnostic unit $\psi(k)$, where $\psi$: \{1, ..., K\} $ \rightarrow \Lambda$ maps each biomarker $k$ to a unique agnostic unit $l \in \Lambda$, where $\Lambda$ is the set of agnostic units. These definitions allow us to formulate the likelihood for a single measurement $y_{ijk}$ as follows:

@@

We trained DKT on ADNI data from the TADPOLE challenge (Marinescu et al., arXiv, 2018), since it contained a large number of multimodal biomarkers already pre-processed and aggregated into one table. From the TADPOLE dataset we selected a subset of 230 subjects which had at least one FDG PET, AV45, AV1451 or DTI scan. Most subjects also had MRI scans and cognitive tests. In order to model another disease, we further included 76 PCA subjects from our own centre in the training set, along with 67 tAD and 87 age-matched controls, all of which only had MRI scans.

For both datasets, volumetric measures for each subject have been obtained using the Freesurfer software. For FDG, AV45 and AV1451 PET, we used already extracted SUVR measures from ADNI. For DTI, we used fractional anisotropy (FA) measures from white-matter regions adjacent to each lobe. For every lobe, we averaged the biomarker values for regions of interest within each lobe and regressed out the following covariates: age, gender, total intracranial volume (TIV) and dataset (ADNI vs our own dataset). Finally, we normalised the biomarker values to lie within the [0,1] range.

@@

We presented DKT, a framework that enables, for the first time, joint modelling of biomarker progressions in multiple neurodegenerative diseases simultaneously. The framework allows the inference of biomarker trajectories in rare diseases, for which there is not enough data to allow estimation of such trajectories, and accounts for a different spatial distribution of pathology between distinct phenotypes. This further enables us to understand the complex mechanisms of rare diseases, as well as mechanisms shared between different types of related diseases.

@@

While in this work we have focused on Alzheimer's variants such as tAD and PCA, DKT can also be applied to other progressive neurodegenerative diseases of non-Alzheimer's type such as tauopathies (e.g. Frontotemporal dementia -- FTD), synucleinopathies (e.g. Parkinson's disease -- PD) or other neurodegenerative diseases, and even the normal ageing process. Cognitive tests can also be included in the disease-specific sub-models of DKT, or even allocated in the agnostic units of the regions that are responsible for those tasks, based on previous voxel-based morphometry studies.

%However, some care needs to be exercised when selecting the biomarkers and grouping them into agnostic units, as in some diseases the assumption of disease agnostic dynamics might not hold for some groups of molecular biomarkers. For example, some non-Alzheimer's tauopathies such as Frontotemporal dementia might show tau abnormalities but no corresponding amyloid abnormalities within the same region. In the case of Frontotemporal dementia, we recommend including higher-level biomarkers such as glucose metabolism from FDG, white matter degeneration from DTI or volume from structural MRI, but one should exclude amyloid markers.

@@

As a key direction of further research, DKT can be used to understand novel mechanisms within a disease (e.g. AD variants), as well as across diseases (e.g. AD vs FTD). For AD variants in particular, one can study whether early biomarkers such as amyloid and tau have different dynamics compared to typical AD, and what these differences are. This can be done by choosing different a-priori allocations of biomarkers to agnostic units, for example allocating amyloid and tau into one a shared agnostic unit, or to the disease specific models, thus making them dependent on the disease. The model with the best data fit or predictive power will indicate the most likely mechanism. For distinct neurodegenerative diseases, it is currently unclear where their corresponding event-cascades merge, and the differences in pathological events across brain regions. DKT can be used to answer such questions, by exploring different allocations of upstream biomarkers to such agnostic units, while differences across brain regions can be studied using DKT's region-specific dysfunctionality scores.

@@

\bibitem{lorenzi2017disease}
Lorenzi, M., Filippone, M., Alexander, D.C. and Ourselin, S., 2017. Disease Progression Modeling and Prediction through Random Effect Gaussian Processes and Time Transformation. arXiv preprint arXiv:1701.01668.

\bibitem{oxtoby2018}
Oxtoby, N.P., Young, A.L., Cash, D.M., Benzinger, T.L., Fagan, A.M., Morris, J.C., Bateman, R.J., Fox, N.C., Schott, J.M. and Alexander, D.C., 2018. Data-driven models of dominantly-inherited Alzheimer's disease progression. bioRxiv, p.250654.

@@

\bibitem{marinescu2018tadpole}
Marinescu, R.V., Oxtoby, N.P., Young, A.L., Bron, E.E., Toga, A.W., Weiner, M.W., Barkhof, F., Fox, N.C., Klein, S. and Alexander, D.C., 2018. TADPOLE Challenge: Prediction of Longitudinal Evolution in Alzheimer's Disease. arXiv preprint arXiv:1805.03909.

>>>>

\begin{abstract}
We introduce Disease Knowledge Transfer (DKT), a novel technique for transferring biomarker information between related neurodegenerative diseases. DKT infers robust multimodal biomarker trajectories in rare neurodegenerative diseases even when only limited, unimodal data is available, by transferring information from larger multimodal datasets from common neurodegenerative diseases. DKT is a joint-disease generative model of biomarker progressions, which exploits biomarker relationships that are shared across diseases. As opposed to current deep learning approaches, DKT is interpretable, which allows us to understand underlying disease mechanisms, and can also predict the future evolution of subjects instead of solving simpler control vs diseased classification tasks. Here we demonstrate DKT on Alzheimer's disease (AD) variants and its ability to predict trajectories for multimodal biomarkers in Posterior Cortical Atrophy (PCA), in lack of such data from PCA subjects. For this we train DKT on a combined dataset containing subjects with two distinct diseases and sizes of data available: 1) a larger, multimodal typical AD dataset (tAD) from the TADPOLE Challenge, and 2) a smaller unimodal Posterior Cortical Atrophy (PCA) dataset from our own centre, for which only a limited number of Magnetic Resonance Imaging (MRI) scans are available. We first show that the estimated multimodal trajectories in PCA are plausible as they agree with previous literature. We further validate DKT in two situations: (1) on synthetic data, showing that it can accurately estimate the ground truth parameters and (2) on 20 DTI scans from controls and PCA patients, showing that it has favourable predictive performance compared to standard approaches. While we demonstrated DKT on Alzheimer's variants, we note DKT is generalisable to other forms of related neurodegenerative diseases.

@@

The estimation of accurate biomarker signatures in Alzheimer's disease (AD) and related neurodegenerative diseases is crucial for understanding underlying disease mechanisms, predicting subjects' progressions, and enrichment in clinical trials. Recently, data-driven disease progression models were proposed to reconstruct long term biomarker signatures from collections of short term individual measurements \cite{lorenzi2017disease,oxtoby2018,jedynak2012computational}. When applied to large datasets of typical AD, disease progression models have shown important benefits in understanding the earliest events in the AD cascade \cite{oxtoby2018}, quantifying biomarkers' heterogeneity \cite{young2018uncovering} and they showed improved predictions over standard approaches \cite{oxtoby2018}. However, by necessity these models require large datasets -- in addition they should be both multimodal and longitudinal. Such data is not always available in rare neurodegenerative diseases. In particular, most datasets for rare neurodegenerative diseases come from local clinical centres, are unimodal (e.g. MRI only) and limited both cross-sectionally and longitudinally -- this makes the application of disease progression models extremely difficult.  Moreover, such a model estimated from common diseases such as typical AD may not generalise to specific variants. For example, in Posterior Cortical Atrophy (PCA) -- a neurodegenerative syndrome causing visual disruption -- posterior regions such as the occipital lobe are affected early, instead of the hippocampus and temporal regions in typical AD.

The problem of limited data in medical imaging has so far been addressed through transfer learning methods. These were successfully used to improve the accuracy of AD diagnosis \cite{hon2017towards} or prediction of MCI conversion \cite{cheng2015domain}, but have two key limitations. First, they use deep learning or other machine learning methods, which are not interpretable and don't allow us to understand underlying disease mechanisms that are either specific to rare diseases, or shared across related diseases. Secondly, these models cannot be used to forecast the future evolution of subjects at risk of disease, which is important for selecting the right subjects in clinical trials.

We propose Disease Knowledge Transfer (DKT), a generative joint model that estimates continuous multimodal biomarker progressions for multiple diseases simultaneously -- including rare neurodegenerative diseases -- and which inherently performs transfer learning between the modelled phenotypes. This is achieved by exploiting biomarker relationships that are shared across diseases, whilst accounting for differences in the spatial distribution of brain pathology. DKT is interpretable, which allows us to understand underlying disease mechanisms, and can also predict the future evolution of subjects at risk of diseases. We apply DKT on Alzheimer's variants and demonstrate its ability to predict non-MRI trajectories for patients with Posterior Cortical Atrophy, in lack of such data. This is done by fitting DKT to two datasets simultaneously: (1) the TADPOLE Challenge \cite{marinescu2018tadpole} dataset containing subjects from the Alzheimer's Disease Neuroimaging Initiative (ADNI) with MRI, FDG-PET, DTI, AV45 and AV1451 scans and (2) MRI scans from patients with Posterior Cortical Atrophy from our own centre. We first show that the estimated trajectories for PCA and tAD subjects are plausible as they agree with previous literature findings. We further validate DKT on simulated data from two synthetic diseases with known ground truth, and a set of 20 DTI scans from controls and PCA patients, showing it yields favourable performance compared to standard approaches. Code for DKT is available online: (URL not shown yet for anonymity).

\begin{figure}[h]
 \centering
 \includegraphics[width=0.9\textwidth,trim=0 0 0 0,clip]{figures/disease_knowledge_transfer_symbols.pdf}
 \caption{Diagram of the proposed DKT framework. We assume that each disease can be modelled as the evolution of abstract dysfunction scores (Y-axis, top row), each one related to different brain regions. Each region-specific dysfunction score then further models (X-axis, bottom row) the progression of several modality-specific biomarkers within that same region. For instance, the temporal dysfunction, modelled as a biomarker in the disease specific model (top row), is the X-axis in the disease agnostic model (temporal unit, bottom row), which aggregates together abnormality from amyloid, tau and MR imaging within the temporal lobe. The biomarker relationships within the bottom units are assumed to be disease agnostic and shared across all diseases modelled. Disease knowledge transfer can then be achieved via the disease-agnostic units. Mathematical notation from section \ref{sec:method} is shown in red to ease understanding.}
 \label{fig:diagram}
\end{figure}

@@

The assumption that the dynamics of some biomarkers are disease-agnostic (i.e. shared across diseases), is key to DKT. There are several reasons why we can make this assumption. First of all, pathology in many related neurodegenerative diseases ( e.g. Alzheimer's variants) are hypothesised to share the same underlying mechanisms (e.g. amyloid and tau accumulation), and within one region, such accumulation leads to the same pathology dynamics across all the related disease variants: hypometabolism (FDG PET), neuronal damage (T1/DTI MRI) and region-specific cognitive decline \cite{jack2010hypothetical} -- the difference between these variants is that distinct brain regions are affected at different times and with different pathology rates and extent, likely caused by selective vulnerability of networks within these regions \cite{seeley2009neurodegenerative}. Secondly, even if the diseases share different upstream mechanisms (e.g. amyloid vs tau accumulation), downstream biomarkers measuring hypometabolism, white matter degradation and structural markers follow the same pathological cascade and will have similar dynamics across diseases.

@@

\begin{equation}
\label{eqDysfunctionScoreDef}
 \gamma_i^l = f(\beta_i + m_{ij}; \lambda_{d_i}^l)
\end{equation}
where $f$ is a smooth monotonic function mapping each disease stage to a dysfunction score, having parameters $\lambda_{d_i}^l$ corresponding to agnostic unit $l \in \Lambda$, where $\Lambda$ is the set of all agnostic units. Moreover, $d_i \in \mathbb{D}$ represents the index of the disease corresponding to subject $i$, where $\mathbb{D}$ is the set of all diseases modelled. For example, MCI and tAD subjects from ADNI as well as tAD subjects from our own cohort can all be assigned $d_i=1$, while PCA subjects from our own centre can be assigned $d_i=2$.  We implement $f$ as a parametric sigmoidal curve similar to \cite{jedynak2012computational}, to enable a robust optimisation and because this accounts for floor and ceiling effects present in AD biomarkers. Variable $\epsilon_k$ denotes the variance of measurements for biomarker $k$.

@@

We model the biomarker dynamics that are disease-agnostic, by constructing the mapping from the dysfunction scores $\gamma_i^l$ to the biomarker measurements. We assume a set of given biomarker measurements $Y = [y_{ijk} | (i,j,k) \in \Omega]$ for subject $i$ at visit $j$ in biomarker $k$, where $\Omega$ is defined as the set of available biomarker measurements, since subjects can have missing biomarkers at various visits. We further denote by $\theta_k$ the trajectory parameters for biomarker $k \in K$ within its agnostic unit $\psi(k)$, where $\psi$: \{1, ..., K\} $ \rightarrow \Lambda$ maps each biomarker $k$ to a unique agnostic unit $l \in \Lambda$. These definitions allow us to formulate the likelihood for a single measurement $y_{ijk}$ as follows:

@@

We trained DKT on ADNI data from the TADPOLE challenge \cite{marinescu2018tadpole}, since it contained a large number of multimodal biomarkers already pre-processed and aggregated into one table. From the TADPOLE dataset we selected a subset of 230 subjects which had at least one FDG PET, AV45, AV1451 or DTI scan. Most subjects also had MRI scans and cognitive tests. In order to model another disease, we further included 76 PCA subjects from our own centre in the training set, along with 67 tAD and 87 age-matched controls, all of which only had MRI scans.

For both datasets, we computed multimodal biomarker measurements corresponding to each brain lobe: MRI volumes using the Freesurfer software, FDG-, AV45- and AV1451-PET standardised uptake value ratios (SUVR) extracted with the standard ADNI pipeline, and DTI fractional anisotropy (FA) measures from white-matter regions adjacent to each lobe. For every lobe, we regressed out the following covariates: age, gender, total intracranial volume (TIV) and dataset (ADNI vs our own dataset). Finally, we normalised the biomarker values to lie within the [0,1] range. For each lobe, we allocated all multimodal biomarkers corresponding to that lobe to its own agnostic unit.

@@

We presented DKT, a framework that enables, for the first time, joint modelling of biomarker progressions in multiple neurodegenerative diseases simultaneously. The framework allows the inference of biomarker trajectories in rare diseases, for which there is not enough data to allow estimation of such trajectories, and accounts for a different spatial distribution of pathology between distinct phenotypes. Our approach is also interpretable, enabling us to understand complex mechanisms underpinning these diseases.

@@

While here we have focused on Alzheimer's variants such as tAD and PCA, DKT can also be applied to other progressive neurodegenerative diseases of non-Alzheimer's type and even the normal ageing process. While we only used imaging data, cognitive tests can also be included in the disease-specific sub-models of DKT, or even allocated in the agnostic units of the regions that are responsible for those tasks.

@@

As a key direction of further research, DKT can be used to understand novel mechanisms within a disease (e.g. AD variants), as well as across diseases (e.g. AD vs FTD). For AD variants in particular, one can study whether early biomarkers such as amyloid and tau have different dynamics compared to typical AD, and what these differences are. This can be done by choosing different a-priori allocations of biomarkers to agnostic units -- e.g. allocating amyloid and tau into one a shared agnostic unit, or otherwise directly to the disease specific models, thus making them dependent on the disease. The model with the best data fit or predictive power will indicate the most likely mechanism. For distinct neurodegenerative diseases, it is also currently unclear where their corresponding event-cascades merge, and the differences in pathological events across brain regions. DKT can be used to answer such questions, by exploring different allocations of upstream biomarkers to such agnostic units.

@@

\bibitem{lorenzi2017disease}
Lorenzi, M., Filippone, M., Frisoni, G.B., Alexander, D.C., Ourselin, S. and Alzheimer's Disease Neuroimaging Initiative, 2017. Probabilistic disease progression modeling to characterize diagnostic uncertainty: application to staging and prediction in Alzheimer's disease. NeuroImage.

\bibitem{oxtoby2018}
Oxtoby, N.P., Young, A.L., Cash, D.M., Benzinger, T.L., Fagan, A.M., Morris, J.C., Bateman, R.J., Fox, N.C., Schott, J.M. and Alexander, D.C., 2018. Data-driven models of dominantly-inherited Alzheimer’s disease progression. Brain, 141(5), pp.1529-1544.

@@

\bibitem{marinescu2018tadpole}
Marinescu, R.V., Oxtoby, N.P., Young, A.L., Bron, E.E., Toga, A.W., Weiner, M.W., Barkhof, F., Fox, N.C., Klein, S. and Alexander, D.C., 2018. TADPOLE Challenge: Prediction of Longitudinal Evolution in Alzheimer's Disease. arXiv:1805.03909.
